### 2013-11-11 src2/thesis.tex
spell pass

Obsidian is an embedded language for general purpose programming of GPUs. We try to strike 
a balance between high level, productivity increasing abstractions and low-level 
control needed for performance. The Obsidian programming model mirrors the GPU arhcitecture 
and the programmer is constrained into writing GPU-friendly code. By supplying hierarchy level 
polymorphic library functions, these constraints does not feel obtrusive. Obsidian programs are 
compiled into CUDA C code. This compilation is based on a simple and elegant monad reification 
technique.

@@

I have often turned to Emil Axelsson with technical questions and he has always been
happy to help. For this I am grateful.

@@

Finally I want to thank my family and friends. Thanks to my sisters and parents for their support.
I thank my friends for being understanding during times when I have been very self-absorbed. 
I am very grateful to my wife Andrea for supporting and believing in me and our daughter Noemi 
for bringing much joy to my breaks from work while writing this thesis; soon she is old enough 
for real LEGO.

>>>>

Obsidian is an embedded language for general purpose programming of GPUs. We try to strike 
a balance between high level, productivity increasing abstractions and low-level 
control needed for performance. The Obsidian programming model mirrors the GPU architecture 
and the programmer is constrained into writing GPU-friendly code. By supplying hierarchy level 
polymorphic library functions, these constraints does not feel obtrusive. Obsidian programs are 
compiled into CUDA C code. This compilation is based on a simple and elegant monad reification 
technique.

@@

I have often turned to Emil Axelsson with technical questions, and he has always been
happy to help. For this I am grateful.

@@

Finally I want to thank my family and friends. Thanks to my sisters and parents for their support.
I thank my friends for being understanding during times when I have been very self-absorbed. 
I am very grateful to my wife Andrea for supporting and believing in me and to our daughter Noemi 
for bringing much joy to my breaks from work while writing this thesis; soon she is old enough 
for real LEGO.
